Multisensor Architecture for an Intersection Management System

### 2018-06-07 ch5-conclusions.tex
Added draft of chapter 5 - conclusions

\section{Summary}
\section{Limitations}
\section{Future Work}
\section{Contributions}
\section{Final Remarks}

>>>>

\section{General Conclusions}
\section{Contributions}

A scalable, modular system for traffic control monitoring at intersection. Both for experimentation and real deployment.

Set of software repositories for application and for available datasets containing intersection data.

Pair of articles submmited to events, one for architecture description and example implementation and another for application comparison.

\section{Future Work}

Generation of our own dataset.

Optimization of communication scheme.

Integration of new types of sensors

Creation of a more friendly user interface.
